Supplementary Materials- A Bayesian networks approach to infer social changes from burials in northeastern Taiwan during the European colonization period

### 2021-08-21 analysis/paper/supplementary-material.Rmd
edit the SI at the proof stage

---
title: "Supplementary Materials- A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period"
author:
  - Li-Ying Wang
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
---

@@

Examples include exploring the political centralization in the Kofun period in Japan through the hierarchical communication network constructed by prestige goods [@Mizoguchi2013], and the investigation of long term inter-site relationships from the Epipalaeolithic to the early Neolithic in the Near East according to trade items [@Coward2013]. Regarding burials, @Sosna2013 examined spatial patterns of burials from the Early Bronze Age in Rebesovice with two hypothesized networks constructed according to cultural and chronological similarity between burials. Recently, complex network modeling has been used to evaluate networks at both node and graph level through simulations of particular processes and statistically tests of the formation of network properties [@Brughmans2013; @Brughmans2018; @Freeman2004; @Salvini2010]. Such applications include simulations and testing of food exchange modes for Ancestral Pueblos on the aggregation of households in the American Southwest [@Crabtree2015], and exploring the diffusion of fired bricks across Hellenistic Europe by comparing similarity networks of sites with random networks [@Ostborn2015]. Another example is the assessment of hunter-gatherer exchange networks structure across the Kuril Islands using bootstrap simulation based on ceramic composition [@Gjesfjeld2015].

@@

We conducted a sensitivity analysis to understand the effect of the prior specification on our two models. We set all the priors to be vague normal distribution (mean is 0 with standard deviation is 10) and a range of plausible priors (mean from 0 to 5 and standard deviation from 0 to 10). The comparison demonstrates that our results are robust to different priors that preserve the differences between our two models, especially for density, transitivity, and centralization. However, the posterior estimates in 95% confidence intervals could vary for some covariates with different priors. In general, models with our informative priors have a better convergence of the MCMC presented by the diagnostic plots.

@@

```{r figure-bgof-pre-E, fig.cap = "Goodness-of-fit diagnostics for the pre-European model and the post-European model (below). Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and black lines show the 95% intervals."}
knitr::include_graphics(here::here("analysis/figures/003-pre-bgof.png"))
```

>>>>

---
title: "Supplementary Materials- A Bayesian networks approach to infer social changes from burials in northeastern Taiwan during the European colonization period"
author:
  - Li-Ying Wang
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
---

@@

Examples include exploring the political centralization in the Kofun period in Japan through the hierarchical communication network constructed by prestige goods [@Mizoguchi2013], and the investigation of long term inter-site relationships from the Epipalaeolithic to the early Neolithic in the Near East according to trade items [@Coward2013]. Regarding burials, @Sosna2013 examined spatial patterns of burials from the Early Bronze Age in Rebesovice with two hypothesized networks constructed according to cultural and chronological similarity between burials. Recently, complex network modeling has been used to evaluate networks at both node and graph level through simulations of particular processes and statistical tests of the formation of network properties [@Brughmans2013; @Brughmans2018; @Freeman2004; @Salvini2010]. Such applications include simulations and testing of food exchange modes for Ancestral Pueblos on the aggregation of households in the American Southwest [@Crabtree2015], and exploring the diffusion of fired bricks across Hellenistic Europe by comparing similarity networks of sites with random networks [@Ostborn2015]. Another example is the assessment of hunter-gatherer exchange networks structure across the Kuril Islands using bootstrap simulation based on ceramic composition [@Gjesfjeld2015].

@@

We conducted a sensitivity analysis to understand the effect of the prior specification on our two models. To explore the sensitivity, we ran the analysis with prior values to be vague normal distribution (mean is 0 with standard deviation is 10) and a range of plausible priors (mean ranging from 0 to 5 and standard deviation ranging from 0 to 10). We found very minor differences in the posterior distributions, but the directionality was consistent for all values. The results of these are not shown here. We choose the priors that have the best autocorrelation properties. The comparison demonstrates that our results are robust to different priors that preserve the differences between our two models, especially for density, transitivity, and centralization. However, the posterior estimates in 95% confidence intervals could vary for some covariates with different priors. In general, models with our informative priors have a better convergence of the MCMC presented by the diagnostic plots.

@@

```{r figure-bgof-pre-E, fig.cap = "Goodness-of-fit diagnostics for the pre-European model. Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and black lines show the 95% intervals."}
knitr::include_graphics(here::here("analysis/figures/003-pre-bgof.png"))
```
